---
title: "List, Loops, and Data frame (W4)"
date: '2019-10-03'
output:
    html_document:
        number_sections: no
        theme: united
        highlight: tango
        toc: yes
        toc_float:
            collapsed: no
        css: style.css
        md_extensions: +implicit_figures
        includes:
            in_header: "../GA.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T,
                      results = 'hide',
                      comment = '#>',
                      message = F)
```



```{js echo=FALSE}
window.onload = () => {
        document.querySelectorAll('.hide').forEach(ele => {
            ele.className = 'note';
        })
}
```

## list

<div class="hide" data-tag="Why lists?">
1. Vector 只能儲存相同資料類型
1. list 能儲存**不同資料類型** (各種 vector)
1. list: hierarchical structure
</div>


<div class="hide" data-tag="list Demo">

1. Create a list

    ```{r}
    list(20, FALSE, c("ig", "selfie"))
    list(age = 20, single = FALSE, tags = c("ig", "selfie"))
    
    # Nested structure
    lst1 <- list(1:3, TRUE)
    list('hello', lst1)
    ```
2. Subset (篩選)
    
    ```{r}
    ben <- list(age = 20, single = FALSE, tags = c("ig", "selfie"))
    ben[1:2]
    ben[c(T, F, T)]
    ben['single']
    ```

    - vector `[]` --> vector; list `[]` --> list; df `[]` --> df
    
    ```{r}
    ben['tags']
    ben[['tags']]
    ```
    
    - **slide**: list as a train analogy
        - 將 list 想像成一輛火車，一個 list 裡面的元素 **的值**儲存在火車的車廂**之內**
        
    - Pop Quiz
</div>


<div class="hide" data-tag="Nested Structure">
```{r}
a_lst <- list(name = "ben",
              info = list(age = 20,
                          tags = c("ig", "selfie")))

# Get "selfie"
a_lst[['info']]
a_lst[['info']][['tags']]
a_lst[['info']][['tags']][1]

a_lst$info
a_lst$info$tags
a_lst$info$tags[2]
```
</div>

**3 min**

## for loop

<div class="hide" data-tag="For Loop">
1. Basics

    ```{r}
    for (elem in 1:3) {
        print(elem)
    }
    
    for (i in 1:5) {
        print(i)
    }
    
    # Use character vector
    vec <- c("謝", "老師", "好", "帥")
    for (word in vec) {
        print(word)
    }
    
    # `if` 遇到最後一個字: 帥
    for (word in vec) {
        print(word)
        
        if (word == "帥") {
            print('真的嗎？')
        }
    }
    ```

2. seq_along

    ```{r}
    # seq_along
    for (i in seq_along(vec)) {
        print(i)
    }
    for (i in seq_along(vec)) {
        print(vec[i])
    }
    
    # rewrite 遇到最後一個字
    for (i in seq_along(vec)) {
        print(vec[i])
        
        if (i == length(vec)) {
            print('真的嗎？')
        }
    }
    ```

3. names

    ```{r}
    vec <- c(Monday = "rainy", Tuesday = "cloudy", Wednesday = "sunny")
    names(vec)

    for (name in names(vec)) {
        sentence <- paste0(name, ' was ', vec[name], '.')
        print(sentence)
    }
    ```
</div>

**3 min**

## Building a for loop

<div class="hide" data-tag="Wrap up: building a for loop">

**slide**: building a for loop

1. Always start with **one concrete case**
2. solve one case and then move on

```{r echo=T, results = 'hide'}
member <- list(
    kai = list(age = 40, about = "a professor"),
    jessy = list(age = 20, about = "a cat lover"),
    joy = list(age = 18, about = "a hacker"),
    ben = list(age = 19, about = "a YouTuber")
)
```

**Demo**

1. 觀察 `member`, 印出一個句子
    
    ```{r}
    member[['kai']]
    phrases <- c('kai', member[['kai']]$about, 'should be wise.')
    sentence <- paste0(phrases,  collapse = ', ')  # explain collapse
    ```

2. 抽象化

    1. 使用 `name` 作為 for 變數 --> 將 `'kai'` 改為 `name`
    
    ```{r}
    for (name in names(member)) {
        member[['kai']]
        phrases <- c('kai', member[['kai']]$about, 'should be wise.')
        sentence <- paste0(phrases,  collapse = ', ')
    }
    ```
    
    2. 加入 `someone` --> 印看看
  
    ```{r results = 'show'}
    for (name in names(member)) {
        someone <- member[[name]]  # 加入 someone
        phrases <- c(name, someone$about, 'should be wise.')  # 加入 someone
        sentence <- paste0(phrases,  collapse = ', ')
        
        print(sentence)  # print intermediate results
    }
    ```
    
    3. 加入條件式
  
    ```{r results = 'show'}
    for (name in names(member)) {
        someone <- member[[name]]
        
        # Construct phrases from `someone`
        phrases <- c(name, someone$about, 'should be wise.')
        if (someone$age < 35) {
            phrases[3] <- 'is quite young.'
        }
        
        sentence <- paste0(phrases,  collapse = ', ')
        
        print(sentence)
    }
    ```

</div>
